Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex
ref and grid

When the entire filterbank does not fit into the GPU's
constant memory, $P$ passes are necessary to compute all of $z$, where
$$P=\frac{FH}{4 \cdot n\_output\_4s \cdot n\_filter\_r}.$$
In such cases, the number of bytes moved to and from global memory is much higher than
the theoretical lower limit.
\begin{align}
\mathrm{Bytes} = 4&RCDP \nonumber \\
& + 4FHWD \nonumber \\
& + 8(R-H+1)(C-W+1)FP.
\nonumber
% XXX: incrementing requires reading and writing $z$ right? so actually the 4
% above should be an 8? (see related ticket on github for potential
% optimization about this)
\label{eq:bytesP}
\end{align}
These passes make the I/O requirements increase quadratically in $F$ and $H$.
At the same time, the total number of floating-point operations (Eq.~\ref{eq:flops})
is quadratic in $H$ and $W$. In our experiments, we only considered square
filters so in our setting the total number of flops is proportional to $H^4$.

XXX
Arithmetic density with passes.

Critically:
The arithmetic intensity, shared storage, and register requirements
of this kernel change significantly and in a complicated platform-dependent way
with the argument parameters ($R, C, D, F, H, W$) and with the implementation parameters,
especially ``block\_w'', ``block\_h'', ``n\_output\_4s'' and ``n\_filter\_rows.''

\subsection{Reference and Grid}
\label{sec:refgrid}
The reference implementation XXX

% XXX: what is reference?  Why was it chosen?
% DDC: wasn't the reference implementation hand-tuned?
% might also want to say something like:
% Given that parameters were hand-chosen for the reference kernel, no claims are made as to the optimality nor universality of this reference (indeed, different programmers would undoubtedly arrive at different results).  We provide this kernel configuration simply as a reasonable indicator of typical performance made possible by ad hoc experimentation with parameters.

Additionally, \cite{pinto+cox:2011gcg} advocate a particular grid search over
what was estimated to be the most relevant part of the configuration space. This grid iterates over all
combinations of XXX, but leaves the value of XXX at. In our experiments, we call this algorithm the {\em grid} search procedure.
The grid included $72$ points in addition to the reference implementation, for a total of $73$ points.
XXX: isn't 73 prime?? explain this so-called ``grid''.

@@

% =============================================================================
\subsection{Search Algorithms}

The core of any online auto-tuning algorithm (Fig.~\ref{fig:autotune_general}) is the search procedure used to explore the space of implementations.
Our implementation space includes 16000 (XXX) points, too many to search exhaustively for every input configuration.
\cite{cox+pinto:2011gcg} recommends a particular hyper-parameter implementation
based on empirical auto-tuning on several platforms, that achieves good
performance on a variety of GPUs from older-generation cards such as the
8600GT all the way to
current-generation flagship cards such as the GTX 580 and C2070.
We call this configuration the {\em reference} implementation.
% XXX: what is reference?  Why was it chosen?
% DDC: wasn't the reference implementation hand-tuned?
% might also want to say something like:
% Given that parameters were hand-chosen for the reference kernel, no claims are made as to the optimality nor universality of this reference (indeed, different programmers would undoubtedly arrive at different results).  We provide this kernel configuration simply as a reasonable indicator of typical performance made possible by ad hoc experimentation with parameters.

Additionally, \cite{cox+pinto:2011gcg} advocate a particular grid search over
what was estimated to be the most relevant part of the configuration space. This grid iterates over all
combinations of XXX, but leaves the value of XXX at. In our experiments, we call this algorithm the {\em grid} search procedure.
The grid included $72$ points in addition to the reference implementation, for a total of $73$ points.
XXX: isn't 73 prime?? explain this so-called ``grid''.

>>>>

When the entire filterbank does not fit into the GPU's
constant memory, $P$ passes are necessary to compute all of $z$, where
$$P=\frac{FH}{4 \cdot n\_output\_4s \cdot n\_filter\_r}.$$
In such cases, the number of bytes moved to and from global memory is much higher than
the theoretical lower limit.
\begin{align}
\mathrm{Bytes} = 4&RCDP \nonumber \\
& + 4FHWD \nonumber \\
& + 8(R-H+1)(C-W+1)FP.
\nonumber
\label{eq:bytesP}
\end{align}
These passes make the I/O requirements increase quadratically in $F$ and $H$.
At the same time, the total number of floating-point operations (Eq.~\ref{eq:flops})
is quadratic in $H$ and $W$. In our experiments, we only considered square
filters so in our setting the total number of flops is proportional to $H^4$.

Critically:
what makes this kernel interesting as a case study is that the
arithmetic intensity, shared storage, and register requirements
of this kernel change significantly and in a complicated platform-dependent way
with the argument parameters ($R, C, D, F, H, W$) and with the implementation parameters,
especially ``block\_w'', ``block\_h'', ``n\_output\_4s'' and ``n\_filter\_rows.''

\subsection{Reference and Grid}
\label{sec:refgrid}

\cite{pinto+cox:2011gcg} recommends as a reference implementation: block\_w 8, 
block\_h = 8, n\_filter\_rows 1, n\_output\_4s all, spill $False$, imul\_fast $True$,
pad\_shared $True$, 
text1dfetch $True$,
maxrregcount $\infty$,
and fast\_math $False$.
This reference implementation was chosen manually based on good performance across a range of platforms from older-generation
cards such as the
8600GT all the way to
current-generation flagship cards such as the GTX 580 and C2070.
Given that parameters were hand-chosen for the reference kernel, no claims are
made as to the optimality nor universality of this reference (indeed, different
programmers would undoubtedly arrive at different results).  We use this
kernel configuration as a reasonable indicator of typical performance
made possible by ad hoc experimentation with parameters.

Additionally, \cite{pinto+cox:2011gcg} advocate a particular grid search over
what was estimated to be the most relevant part of the configuration space.
This grid iterates over all
combinations of n\_filter\_rows, n\_output\_4s, spill\_l, pad\_shared\_l for three different block\_h, block\_w choices: (16, 8), (16, 16), and (32, 8).
In our experiments, we call this algorithm the {\em grid} search procedure.
The grid included $72$ points in addition to the reference implementation, for a total of $73$ points.

@@

% =============================================================================
Additionally, \cite{cox+pinto:2011gcg} advocate a particular grid search over
what was estimated to be the most relevant part of the configuration space. This grid iterates over all
combinations of XXX, but leaves the value of XXX at. In our experiments, we call this algorithm the {\em grid} search procedure.
The grid included $72$ points in addition to the reference implementation, for a total of $73$ points.
XXX: isn't 73 prime?? explain this so-called ``grid''.
